Artistic Curve Steganography Carried by Musical Audio

### 2022-11-17 writeup/paper.tex
Finished papergit add -u!

As for most other steganographic carriers, the simplest techniques for audio steganography rely on changing the least significant bit of uncompressed encodings (e.g. \cite{cvejic_wavelet_2002}).  Other early works rely on the ``frequency masking'' property of the human auditory system.  Binary data is stored by controlling the relative amplitude of two frequencies that are masked in this way \cite{gopalan_unified_2009, gopalan2004audio}.

@@

then it is possible to perform a swap to yield a new tour with a smaller distance.  This amounts to reversing the indices in the tour between index $i+1$ and $j$, inclusive.  We repeat this step as long as such a swap is still possible.  Though this is not guaranteed to yield an optimal TSP tour, it does produce tours which are simple; that is, every crossing is removed.% (Figure~\ref{fig:TwoOpt}).

@@

\subsubsection{The choice of non-overlapping windows}
Though some other works use transforms with overlapping windows \cite{hwan_sik_yun_acoustic_2010,geleta_pixinwav_2021}, changing different STFT bins independently leads to STFTs that do not correspond to any real signal due to discrepancies between overlapping windows.  An algorithm like Griffin-Lim \cite{griffin1984signal} can recover a signal whose spectrogram has a locally minimal distance to the perturbed STFT, but we find that this step introduces an unacceptable level of distortion both in the target and the carrier audio.  This problem occurs even for real-valued transforms such as the Discrete Cosine Transform (which was used by \cite{geleta_pixinwav_2021}).  Like \cite{xiaoxiao_dong_data_2004}, we sidestep this problem by using non-overlapping windows.

@@

Beyond shifting and scaling the targets coordinates vertically, we may also need to re-parameterize them in time, since, in general, the SWS-STFT sequence will not have the same number of samples as the shifted target $\hat{T}$.  Furthermore, the target curves are cyclic, so the starting point is arbitrary, nor does it matter if we traverse the curve left or right.  This gives us a lot of freedom in how we choose to re-parameterize the target to best match the signal even before we perturb the signal.  Let $N_M$ be the number of frames in the SW-STFT and $N_T$ be the number of samples of the target, and assume that $N_T > N_M$ (we can always resample our target curves to make this true).  Let $\Theta = \{ \theta_1, \theta_2, \theta_3, \hdots, \theta_{N_M} \}$ be new indices into the target, and let $K > 0$ be a positive integer so that $1 \leq \left( (\theta_i - \theta_{i-1}) \mod N_T \right) \leq K$; that is, $K$ is the maximum number of samples by which the target re-parameterization can jump in adjacent time steps.  We seek a $\Theta$ minimizing the following objective function for a $d$-dimensional shifted target $\hat{T}$

@@

We now quantitatively assess the performance of our system.  To generate a large set of curves, we generate TSP art on the roughly 10,000 images in the Caltech-101 dataset  \cite{li_andreeto_ranzato_perona_2022} (e.g. Figure~\ref{fig:caltech101examples}), and we generate Hamiltonian cycles on the 380 watertight triangle meshes in the Princeton mesh segmentation database \cite{Chen:2009:ABF} (e.g. Figure~\ref{fig:meshsegexamples}).  We then use the 1000 30 second audio clips from the Tzanetakis genre dataset \cite{tzanetakis2002musical} as carrier audio.  For the Caltech-101 database, we partition the images into sets of 10, which are each encoded in one of the audio carriers varying $\lambda$ and $\ell$.  Likewise, for the mesh segmentation dataset, we hide each Hamiltonian path in three different audio clips from the Tzanetakis dataset.  In all cases, we encode the audio using lossy mp3 compression at 64 kbps.

@@

Overall, we see slightly higher distortions and lower SNRs for 3D embeddings than 2D embeddings, which makes sense since there is one additional coordinate to hide.  As expected, increasing $\lambda$ increases both the SNR and distortion, as shown in Figure~\ref{fig:ResultsFixedWin}. Also, as Figure~\ref{fig:ResultsFixedLam} shows, increasing the window length has a positive effect on geometric distortion, while moderate window lengths lead to the best SNR.  We also see a positive effect of the Viterbi alignment from Section~\ref{sec:reparam} on the SNR in Figure~\ref{fig:ResultsViterbiExperiment}.  Finally, we run an experiment on the Caltech-101 dataset by choosing 4 random frame offsets per embedding, and we see in Figure~\ref{fig:ShiftsExperiment} that the algorithm of Section~\ref{sec:framealignments} recovers alignments well.

@@

Though the experiments above are encouraging, SNR can be misleading; frequencies that are more audible may actually have a higher SNR.  To address this, we performed a crowd-sourced listening experiment on the Amazon Mechanical Turk where we embedded a random image from the Caltech-101 dataset in each of the Tzanetakis clips.  We split them into 4 groups with no embedding (control), and with $\lambda = 0.1, 1, 10$, and we asked the listeners to rate the quality of the noise on the 5 point impairment scale of \cite{bassia2001robust} (5: imperceptible, 4: perceptible but not annoying, 3: slightly annoying, 2: annoying, 1: very annoying).  In our experiment, we had 46 unique Turkers, 21 of whom participated in at least 40 rankings.  Figure~\ref{fig:TurkResults} shows the results.  Mean opinion scores (MOS) are correlated with $\lambda$, but there's not much of a difference between $\lambda=0.1$ and $\lambda=1$, which suggests using the former as a rule of thumb due to its lower geometric distortion.
% We see a Pearson correlation of $r=0.48$ between the mean opinion score and the SNR in dB.

@@

\section{Discussion / Conclusion}

@@

>>>>

As is the case for most other steganographic carriers, the simplest techniques for audio steganography rely on changing the least significant bit of uncompressed encodings (e.g. \cite{cvejic_wavelet_2002}).  Other early works rely on the ``frequency masking'' property of the human auditory system.  Binary data is stored by controlling the relative amplitude of two frequencies that are masked in this way \cite{gopalan_unified_2009, gopalan2004audio}.

@@

then it is possible to perform a swap to yield a new tour with a smaller distance.  This amounts to reversing the indices in the tour between index $i+1$ and $j$, inclusive.  We repeat this step as long as such a swap is still possible.  Though this is not guaranteed to yield an optimal TSP tour, it does produce aesthetically pleasing tours which are simple; that is, every crossing is removed.% (Figure~\ref{fig:TwoOpt}).

@@

\subsubsection{The choice of non-overlapping windows}
Though some other works use transforms with overlapping windows \cite{yun2009acoustic,geleta_pixinwav_2021}, changing different STFT bins independently leads to STFTs that do not correspond to any real signal due to discrepancies between overlapping windows.  An algorithm like Griffin-Lim \cite{griffin1984signal} can recover a signal whose spectrogram has a locally minimal distance to the perturbed STFT, but we find that this step introduces an unacceptable level of distortion both in the target and the carrier audio.  This problem occurs even for real-valued transforms such as the Discrete Cosine Transform (which was used by \cite{geleta_pixinwav_2021}).  Like \cite{xiaoxiao_dong_data_2004}, we sidestep this problem by using non-overlapping windows.

@@

Beyond shifting and scaling the targets coordinates vertically, we may also need to re-parameterize them in time, since, in general, the SWS-STFT sequence will not have the same number of samples as the shifted target $\hat{T}$.  Furthermore, the target curves are cyclic, so the starting point is arbitrary, nor does it matter if we traverse the curve left or right, or at a constant speed.  This gives us a lot of freedom in how we choose to re-parameterize the target to best match the signal even before we perturb the signal.  Let $N_M$ be the number of frames in the SW-STFT and $N_T$ be the number of samples of the target, and assume that $N_T > N_M$ (we can always resample our target curves to make this true).  Let $\Theta = \{ \theta_1, \theta_2, \theta_3, \hdots, \theta_{N_M} \}$ be new indices into the target, and let $K > 0$ be a positive integer so that $1 \leq \left( (\theta_i - \theta_{i-1}) \mod N_T \right) \leq K$; that is, $K$ is the maximum number of samples by which the target re-parameterization can jump in adjacent time steps.  We seek a $\Theta$ minimizing the following objective function for a $d$-dimensional shifted target $\hat{T}$

@@

We now quantitatively assess the performance of our system.  To generate a large set of curves, we generate TSP art on the roughly 10,000 images in the Caltech-101 dataset  \cite{li_andreeto_ranzato_perona_2022} (e.g. Figure~\ref{fig:caltech101examples}), and we generate Hamiltonian cycles on the 380 watertight triangle meshes in the Princeton mesh segmentation database \cite{Chen:2009:ABF} (e.g. Figure~\ref{fig:meshsegexamples}).  We then use the 1000 30 second audio clips from the Tzanetakis genre dataset \cite{tzanetakis2002musical} as carrier audio.  For the Caltech-101 database, we partition the images into sets of 10, which are each encoded in one of the audio carriers varying $\lambda$ and $\ell$.  Likewise, for the mesh segmentation dataset, we hide each Hamiltonian path in three different audio clips from the Tzanetakis dataset.  In all cases, we use an STFT window length of 1024 at a sample rate of 44100hz, and we encode the audio using lossy mp3 compression at 64 kbps.

@@

Overall, we see slightly higher distortions and lower SNRs for 3D embeddings than 2D embeddings, which makes sense since there is one additional coordinate to hide.  As expected, increasing $\lambda$ increases both the SNR and distortion, as shown in Figure~\ref{fig:ResultsFixedWin}. Also, as Figure~\ref{fig:ResultsFixedLam} shows, increasing the window length has a positive effect on geometric distortion, while moderate window lengths lead to the best SNR.  We also see a positive effect of the Viterbi alignment from Section~\ref{sec:reparam} on the SNR in Figure~\ref{fig:ResultsViterbiExperiment}.  Though $\approx$+1dB may not seem significant, it can make a huge difference in audio, particularly in quiet regions.  Finally, we run an experiment on the Caltech-101 dataset by choosing 4 random frame offsets per embedding, and we see in Figure~\ref{fig:ShiftsExperiment} that the algorithm of Section~\ref{sec:framealignments} recovers alignments well.

@@

Though the experiments above are encouraging, SNR can be misleading; frequencies that are more audible may actually have a higher SNR due to psychoacoustic phenomena.  To address this, we performed a crowd-sourced listening experiment on the Amazon Mechanical Turk where we embedded a random image from the Caltech-101 dataset in each of the Tzanetakis clips.  We split them into 4 groups with no embedding (control), and with $\lambda = 0.1, 1, 10$, and we asked the listeners to rate the quality of the noise on the 5 point impairment scale of \cite{bassia2001robust} (5: imperceptible, 4: perceptible but not annoying, 3: slightly annoying, 2: annoying, 1: very annoying).  In our experiment, we had 46 unique Turkers, 21 of whom participated in at least 40 rankings.  Figure~\ref{fig:TurkResults} shows the results.  Mean opinion scores (MOS) are correlated with $\lambda$, but there's not much of a difference between $\lambda=0.1$ and $\lambda=1$, which suggests using the former as a rule of thumb due to its lower geometric distortion.
% We see a Pearson correlation of $r=0.48$ between the mean opinion score and the SNR in dB.

@@

\section{Discussion / Supplementary Material}

@@

To show off our pipeline, we created an interactive viewer in Javascript using WebGL that can load in and decode any mp3 file.  The viewer plays the decoded curve synchronized to the music.  We also provide a variety of 2D and 3D examples.  To view our source code for encoding and decoding and look at these examples, please visit \url{https://curvesteg.s3.amazonaws.com/index.html}
